Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline

### 2017-09-13 draft/response_to_referee.txt

-----
# 8. p. 7-8: "High level reduction pipeline": as stated more clearly in the hscPipe technical paper (Bosch et
al. 2017). Low-level reduction involves basic image detrending and calibration; high-level processes involves
the ones that generate coadded images and science-ready catalogs.  Now use the same explanation here to be
consistent with the technical paper and provide more details.

-----
# 9. "purity and completeness"

We agree with the referee that the purity and completeness tests are very important for
survey like this, and SynPipe can be a useful tool for this purpose.

At the same time, careful tests for this purpose are beyond the scope of this paper, where
we simply want to demonstrate the application of SynPipe and provide simple photometric
benchmark tests for stars and galaxies.

Following the suggestions from the referee, we modify the text with more discussions on
this, and here are the main points:
    - Section 4.2: We explain that it is beyond the scope of this work to look into this
      carefully.  Detection limits and completeness are normally defined for point sources.  
      As we show using the PSF S/N, it depends on the seeing condition and show spatial 
      changes which requires more careful designs and higher density of fake stars. 
      Detection completeness of point sources for HSC DR1 is investigated in Aihara+2017
      (see Section 5.7) using a different method. 
    - The efficiency

@@

We think the location and context of this figure makes it very clear that it is for the input
parameters.  Now we state that clearly in the caption.

----
5. Fig. 4 and 5: has been corrected.

----
6. p.22:

For stars, first, fraction of stars with such extreme colors are very low.  The
discrepency can barely be noticed on the comparisons of 1-D color distributions. 
We think the likely reasons for this are: 
    - There are still scattered light on the y-band images that are not accounted for.
      This known prolblem can affect the accuracy of y-band photometry and is discussed in 
      Section 5.8.14 in Aihara+2017. 
    - Background level is much higher in z and y-band, and background subtraction could
      suffer from higher uncertainties.  Right now, SynPipe can still not test the impact
      of background subtraction on photometry, and it will be investigated in the future. 
    - We modify text in Section 5.1.3 to breifly explain this.

As for galaxies, the same background and y-band scatter light issues also exist.  However,
the dynamical ranges for i-z and z-y colors are narrower.  Also the CModel color
uncertainties are higher than the PSF ones.  Both of these factors make it harder to spot
discrepencies of color distributions.  However, we still see discrenpencies between the
input and recovered z-y colors. 
    - We expand the discussion in Section 5.2.3 a little to address this issue.

----
7. p.22

### 2017-09-13 draft/ms_v5.tex
A few minor comments

    We use a synthetic star sample built using data from the HST/ACS catalog of 
    \citet{Leauthaud2007}.  
    We first select stars from the \citet{Leauthaud2007} catalog (this classification 
    is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag). 
    We then match this sample against our HSC UltraDeep--COSMOS data (which reaches 
    ${\sim}27.2$ mag in $i$ band). 
    After applying basic quality cuts (see \ref{app:qc}), this procedure provides us 
    with five-band HSC PSF photometry for 14,472 stars.
    To increase the sample size, we re-sample the five-band magnitude distributions 
    using the \texttt{astroML} (\citealt{astroml}) implementation of the 
    \texttt{extreme-deconvolution} algorithm developed by \citet{Bovy2011}
    \footnote{\texttt{https://github.com/jobovy/extreme-deconvolution/}} to
    generate 100,000 synthetic stars. 
    Fig \ref{fig:star_sample} shows the magnitude and color distributions of real 
    COSMOS stars compared to the resampled distributions in all five-bands and in 
    color-color space.

@@

    Fig \ref{fig:psf_cdist} displays the precision of PSF colors by comparing the 
    color distributions of the input sample to the recovered color distributions. 
    Using four different colors and two color--color planes, we show that the 
    \forced{} PSF colors accurately recover the distributions of all four colors 
    and the color-color distributions.

@@

    Fig \ref{fig:cmodel_cdist} compare the input color--color distributions with the
    recovered ones. 
    The general 2--D distributions are well recovered but the precision is not as 
    good as for stars, especially in the $(i-z)$ vs. $(z-y)$ plane.
    This is expected given the narrow dynamical ranges of these colors in the redder 
    filters.
    The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$
    colors at the very ``blue'' end, while overestimating the \song{
    $(i-z)$ color}
    at the very red end.

>>>>

    We use a synthetic star sample built using data from the HST/ACS catalog of 
    \citet{Leauthaud2007}.  
    We first select stars from the \citet{Leauthaud2007} catalog (this classification 
    is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag). 
    We then match this sample against our HSC UltraDeep--COSMOS data (which reaches 
    ${\sim}27.2$ mag in $i$ band). 
    After applying basic quality cuts (see \ref{app:qc}), this procedure provides us 
    with five-band HSC PSF photometry for 14,472 stars.
    To increase the sample size, we re-sample the five-band magnitude distributions 
    using the \texttt{astroML} (\citealt{astroml}) implementation of the 
    \texttt{extreme-deconvolution} algorithm developed by \citet{Bovy2011}
    \footnote{\texttt{https://github.com/jobovy/extreme-deconvolution/}} to
    generate 100,000 synthetic stars. 
    Fig \ref{fig:star_sample} shows the magnitude and color distributions of real 
    COSMOS stars compared to the resampled distributions in all five-bands and in 
    color-color space.
    \song{
    It is worth noting that \synpipe{} test using synthetic stars can also help 
    determine the detection limit and point sources completeness of the HSC data. 
    However, both of them depend on seeing or background conditions, and show 
    spatial variations that need to be considered.  
    It normally requires higher density of synthetic objects to carefully test this 
    and is beyond the scope of this work.  
    Please see Section~5.6 and Section~5.7 of \citet{HSCDR1} for investigation of 
    this topic for HSC SSP DR1 using different method.
    }

@@

    Fig \ref{fig:psf_cdist} displays the precision of PSF colors by comparing the 
    color distributions of the input sample to the recovered color distributions. 
    Using four different colors and two color--color planes, we show that the 
    \forced{} PSF colors accurately recover the distributions of all four colors 
    and the color-color distributions.
    \song{
    On the $(i-z)$-$(z-y)$ color plane, stars with extreme colors are not well 
    recovered.  
    Fraction of these stars is very low, and it could relate to the scattered 
    light in $y$-band that is still unaccounted for (see Section~5.8.14 of 
    \citealt{HSCDR1}). 
    }

@@

    Fig \ref{fig:cmodel_cdist} compare the input color--color distributions with the
    recovered ones. 
    The general 2--D distributions are well recovered but the precision is not as 
    good as for stars, especially in the $(i-z)$ vs. $(z-y)$ plane.
    This is expected given the narrow dynamical ranges of these colors in the redder 
    filters.
    The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$
    colors at the very ``blue'' end, while overestimating the \song{
    $(z-y)$ color}
    at the very red end.
    \song{
    The same $y$-band scattered light issue also affects the \cmodel{} photometry. 
    The background levels are also higher in the $z$- and $y$-band, which could lead 
    to higher uncertainties from background subtraction.  
    Unfortunately, \synpipe{} is not yet equipped to test the impact of background 
    subtraction on photometry, and the issues with the $(z-y)$ colors will be 
    investigated later. 
    }
